---
title: "vignettes-hao-qin"
author: "HAO QIN"
date: "2019/5/3"
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(binomial)
```


bin_choose() calculates the choose of binomial distribution

```{r}
bin_choose(n = 5, k = 2)
bin_choose(5, 0) 
bin_choose(5, 1:3)
```

bin_probability() calculates the probability of a binomial distribution

```{r}
## calculate the probability on success times under trials times within certain successful probabilities
bin_probability(success = 2, trials = 5, prob = 0.5)
bin_probability(success = 1:3, trials = 5, prob = 0.5)

```

bin_distribution() calculates the distribution for a binomial distribution
Method plot.bindis() is to graphs a barplot of this distribution
```{r}
bin_distribution(trials = 5, prob = 0.5)
dis1 <- bin_distribution(trials = 5, prob = 0.5) 
plot(dis1)
```

bin_cumulative() calculates the cumulative probability of a binomial distribution
Method plot.bincum() is to graphs the cumulative distribution 
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

bin_variable() creates an object of class "binvar".
Method print.binvar() is to print the content of an object "binvar"
Method summary.binvar() and print.summary.binvar() is to get a summary description of the object
```{r}
bin_variable(trials = 10, p = 0.5)
summary(bin_variable(trials = 10, p = 0.5))
```


Functions of measures 
bin_mean(), bin_variance(),  bin_mode(), bin_skewness(), bin_kurtosis()
  
```{r}
bin_mean(10, 0.3)
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
